---
title: "Lab 9"
author: "Ben Peters"
date: "November 16, 2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(stringr)
library(tidyverse)
```

```{r}
x <- c("apple", "banana", "pear")
str_view(x, "ar")
```

```{r}
str_view(x, ".a.")
```
```{r}
dot <- "\\."
writeLines(dot)
```
```{r}
x <- c("abc", "a.c", "bef")
str_view(x, "a\\.c")
```
```{r}
x <- "a\\b"
writeLines(x)
```
```{r}
str_view(x, "\\\\")
```
Exercise 14.3.1.1 1:
"\" is an escape which will escape to the next character in the string, whereas "\\" will be read as a single escape \ and function in the same way: escapign to the next character in the expression. "\\\" will escape a character in the string that's already been escaped, as it will be read as a \ followed by another \.

```{r}
x <- c("apple", "banana", "pear")
str_view(x, "^a")
```

```{r}
str_view(x, "a$")
```

```{r}
x <- c("apple pie", "apple", "apple cake")
str_view(x, "^apple pie$")
```
Exercise 14.3.2.1 1:
By using the escape symbol \:
```{r}
str_view(c("$^$", "aaab$^$ddd", "adlfkjas"), "^\\$\\^\\$$", match = TRUE)
```


```{r}
x <- c("abc", "a.c", "a*c", "a c")
str_view(x, "a[.]c")
```
```{r}
str_view(x, ".[*]c")
```
```{r}
str_view(x, "a[ ]")
```
```{r}
x <- c("grey", "gray", "gruy")
str_view(x, "gr(e|a)y")
```
14.3.3.1 Exercise 1:
```{r}
str_view(stringr::words, "^[aeiou]")
```

```{r}
str_view(stringr::words, "[aeiou]", match = FALSE)
```

```{r}
str_subset(stringr::words,"[^e]ed$")
```
```{r}
str_subset(stringr::words, "i(ng|se)$")
```

```{r}
x <- "1888 is the longest year in Roman numerals: MDCCCLXXXVIII"
str_view(x, "XX?")
```

```{r}
str_view(x, "XX+")
```

```{r}
str_view(x, 'X[VI]+')
```
```{r}
str_view(x, "C{2}")
```
```{r}
str_view(x, "C{2,}")
```
```{r}
str_view(x, "C{2,}")
```
```{r}
str_view(x, 'C{2,3}?')
```
```{r}
str_view(x, 'C[LX]+?')
```
Exercise 14.3.4.1 1:
?: {0,1} - up to 1
+: {1,} - 1 or more
*: {0,} - 0 or more

```{r}
str_view(fruit, "(..)\\1", match = TRUE)
```
Exercise 14.3.5.1 1:
(.)\1\1 will match characters appearing consecutively three times.

"(.)(.)\\2\\1" will match a palindromic repeat of two characters like "prrp" or "uttu".

(..)\1 will match any two repeated characters.

"(.).\\1.\\1" will match any sequence of five characters in which the third and fifth are the same as the first.

"(.)(.)(.).*\\3\\2\\1" will match a sequence of three characters followed by any character followed by a reversed repeat of the first three characters.

```{r}
x <- c("apple", "banana", "pear")
str_detect(x, "e")
```
```{r}
sum(str_detect(words, "^t"))
```
```{r}
mean(str_detect(words, "[pbtdkg]$"))
```
```{r}
no_vowels_1 <- !str_detect(words, "[aeiou]")
```
```{r}
no_vowels_2 <- str_detect(words, "^[^aeiou]+$")
identical(no_vowels_1, no_vowels_2)
```
```{r}
words[str_detect(words, "x$")]
```
```{r}
str_subset(words, "x$")
```
```{r}
df <- tibble(
  word = words, 
  i = seq_along(word)
)
df %>% 
  filter(str_detect(word, "x$"))
```
```{r}
x <- c("apple", "banana", "pear")
str_count(x, "a")
```
```{r}
mean(str_count(words, "[aeiou]"))
```
```{r}
df %>% 
  mutate(
    vowels = str_count(word, "[aeiou]"),
    consonants = str_count(word, "[^aeiou]")
  )
```
```{r}
str_count("abababa", "aba")
str_view_all("abababa", "aba")
```
Exercise 14.4.1.1 1
Start or end with x:
```{r}
words[str_detect(words, "^x|x$")]
```
```{r}
x_start <- str_detect(words, "^x")
x_end <- str_detect(words, "x$")

words[x_end|x_start]
```

Start w/ vowel, end w/ consonant
```{r}
words[str_detect(words, "^[aeiou].*[bcdfghjklmnpqrstvwxyz]$")]
```
```{r}
vowel_start <- str_detect(words, "^[aeiou]")
con_end <- str_detect(words, "[bcdfghjklmnpqrstvwxyz]$")
words[vowel_start & con_end]
```

Words with at least one of each vowel:
```{r}
aeiou <- 
  cross(rerun(5, c("a", "e", "i", "o", "u")),
    .filter = function(...) {
      x <- as.character(unlist(list(...)))
      length(x) != length(unique(x))
    }
  ) %>%
  map_chr(~str_c(unlist(.x), collapse = ".*")) %>%
  str_c(collapse = "|")
str_subset(words, aeiou)
```
```{r}
words[str_detect(words, "a") &
  str_detect(words, "e") &
  str_detect(words, "i") &
  str_detect(words, "o") &
  str_detect(words, "u")]
```

```{r}
length(sentences)
```

```{r}
head(sentences)
```
```{r}
colours <- c("red", "orange", "yellow", "green", "blue", "purple")
colour_match <- str_c(colours, collapse = "|")
colour_match
```
```{r}
has_colour <- str_subset(sentences, colour_match)
matches <- str_extract(has_colour, colour_match)
head(matches)
```
```{r}
has_colour
```
```{r}
more <- sentences[str_count(sentences, colour_match) > 1]
str_view_all(more, colour_match)
```
```{r}
str_extract(more, colour_match)
```
```{r}
str_extract_all(more, colour_match)
```

```{r}
str_extract_all(more, colour_match, simplify = TRUE)
```
```{r}
x <- c("a", "a b", "a b c")
str_extract_all(x, "[a-z]", simplify = TRUE)
```
14.4.2.1 Exercise 1:
```{r}
colours <- c("red", "orange", "yellow", "green", "blue", "purple")
colour_match_corrected <- str_c("\\b(", str_c(colours, collapse = "|"), ")\\b")
colour_match_corrected
more <- sentences[str_count(sentences, colour_match) > 1]
str_view_all(more, colour_match_corrected)
```
```{r}
noun <- "(a|the) ([^ ]+)"

has_noun <- sentences %>%
  str_subset(noun) %>%
  head(10)
has_noun %>% 
  str_extract(noun)
```
```{r}
has_noun %>% 
  str_match(noun)
```
```{r}
tibble(sentence = sentences) %>% 
  tidyr::extract(
    sentence, c("article", "noun"), "(a|the) ([^ ]+)", 
    remove = FALSE
  )
```
14.4.3.1 Exercise 1:
```{r}
wnum <- "\\b(one|two|three|four|five|six|seven|eight|nine|ten) +(\\w+)"
sentences[str_detect(sentences, wnum)] %>% 
  str_extract(wnum)
```

```{r}
x <- c("apple", "pear", "banana")
str_replace(x, "[aeiou]", "*")
```
```{r}
str_replace_all(x, "[aeiou]", "v")
```

```{r}
x <- c("1 house", "2 cars", "3 people")
str_replace_all(x, c("1" = "one", "2" = "two", "3" = "three"))
```
```{r}
sentences %>% 
  str_replace("([^ ]+) ([^ ]+) ([^ ]+)", "\\1 \\3 \\2") %>% 
  head(5)
```

14.4.4.1 Exercise 1:
```{r}
slash <- c("/sdf/d/fd/sf/ds", "////d/", "adasdfas/d")
slash
```
```{r}
str_replace_all(slash, "/", "\\\\")
```

```{r}
sentences %>%
  head(5) %>% 
  str_split(" ")
```

```{r}
"a|b|c|d" %>% 
  str_split("\\|") %>% 
  .[[1]]
```
```{r}
sentences %>%
  head(5) %>% 
  str_split(" ", simplify = TRUE)
```
```{r}
fields <- c("Name: Hadley", "Country: NZ", "Age: 35")
fields %>% str_split(": ", n = 2, simplify = TRUE)
```
```{r}
x <- "This is a sentence.  This is another sentence."
str_view_all(x, boundary("word"))
```

```{r}
str_split(x, " ")[[1]]
```
```{r}
str_split(x, boundary("word"))[[1]]
```
14.4.5.1 Exercise 1:

```{r}
fruits <- "Apples, pears, and bananas"
str_split(fruits, boundary("word"))
```

